### 2024-10-24 manuscript.tex
Minor edits

The results imply that SO cloud biases are still a substantial issue in the
km-scale resolution ICON model, even though an improvement over the
lower-resolution reanalyses is notable. More effort is needed to improve the
model cloud simulations in this fast-changing and understudied region. The
transition from models with parametrised convection and clouds to
storm-resolving models might not solve these biases without additional
effort. Evaluation of SO ocean--atmosphere heat, moisture, and momentum fluxes
against in situ observations and comparison of GSRM model simulations against
large-eddy simulations are two potential avenues for future research that
could elucidate the physical mechanisms behind the biases, in addition to the
more common efforts in SO cloud microphysics and precipitation evaluation.

>>>>

The results imply that SO cloud biases are still a substantial issue in the
km-scale resolution ICON model, even though an improvement over the
lower-resolution reanalyses is notable. More effort is needed to improve the
model cloud simulations in this fast-changing and understudied region. The
transition from models with parametrised convection and clouds to
storm-resolving models might not solve these biases without additional effort.
Evaluation of ocean--atmosphere heat, moisture, and momentum fluxes against in
situ observations over the SO and comparison of GSRM simulations against
large-eddy simulations are two potential avenues for future research that could
elucidate the physical mechanisms behind the biases, in addition to the more
common efforts in SO cloud microphysics and precipitation evaluation.
